---
title: "Draft for Final Project"
output: html_notebook
Author: "Anjie Cao" 
---


```{r}
library(tidyverse)
```

# Read in raw data 
```{r}
young_raw <- read.csv("/Users/caoanjie/Desktop/Spring2020/DS/_DSPN_S20/FINALPROJECT/CALA_12MO_RAW.csv")
old_raw <- read.csv("/Users/caoanjie/Desktop/Spring2020/DS/_DSPN_S20/FINALPROJECT/CALA_20MO_RAW.csv")

head(young_raw)
head(old_raw)
```
# Data-preprocessing: Select relevant columns and combine them together 

```{r}
young_raw %>% 
  mutate(AgeGroup = "Young") %>% 
  mutate(ID = paste("young", as.character(ID))) %>% 
  mutate(ageByDays = as.Date(as.character(Test.Date), format="%m/%d/%Y") - as.Date(as.character(DOB), format="%m/%d/%Y")) %>% 
  select(ID, Sex, AgeGroup, ageByDays, CDI.SCORE,pretest, blue.neem, black.neem, black.blue.that, blue.black.that, Posttest) %>% 
  rename(label_inconsistent = blue.neem, label_consistent = black.neem, sentence_inconsistent = black.blue.that, sentence_consistent = blue.black.that, posttest = Posttest) %>% 
  gather(trialType, LookingTime, pretest:posttest) %>% 
  mutate(blockType = ifelse(grepl("label", trialType), "label", ifelse(grepl("sentence", trialType),  "sentence", "nontest")),
         consistency = ifelse(grepl("inconsistent", trialType), "inconsistent", ifelse(grepl("consistent", trialType), "consistent","nontest")),
         trialType = ifelse(trialType %in% c("pretest", "posttest"), trialType, "test")) %>% 
  na.omit -> young_raw

old_raw %>% 
  mutate(AgeGroup = "Old") %>% 
  mutate(ID = paste("old", as.character(ID))) %>% 
  mutate(ageByDays = as.Date(as.character(Test.Date), format="%m/%d/%Y") - as.Date(as.character(DOB), format="%m/%d/%Y")) %>% 
  select(ID, Sex, AgeGroup, ageByDays, CDI.SCORE,pretest, blue.neem, black.neem, black.blue.that, blue.black.that, Posttest) %>% 
  rename(label_inconsistent = blue.neem, label_consistent = black.neem, sentence_inconsistent = black.blue.that, sentence_consistent = blue.black.that,posttest = Posttest ) %>% 
  gather(trialType, LookingTime, pretest:posttest) %>% 
 mutate(blockType = ifelse(grepl("label", trialType), "label", ifelse(grepl("sentence", trialType),  "sentence", "nontest")),
         consistency = ifelse(grepl("inconsistent", trialType), "inconsistent", ifelse(grepl("consistent", trialType), "consistent","nontest")),
         trialType = ifelse(trialType %in% c("pretest", "posttest"), trialType, "test")) %>%  
  na.omit -> old_raw

data <- bind_rows(young_raw, old_raw) 
data <- data %>% filter(trialType == "test")
```

# Fit models on the current data:
```{r}
lt_current <- lmer(LookingTime ~ AgeGroup+Sex+blockType+consistency+blockType*consistency+(1|ID), data=data)
summary(lt_current)$coefficients
```



### 

LookingTimeDuration ~ Age + Sex + Consistency + Block + Consistency * Block + (1 | Participant_ID)
	- LookingTimeDuration: continuous, duration of looking toward the screen.
	- Age: categorical variable, 12-month-olds group / 20-month-olds 
	- Sex: categorical variable, F/M
	- Consistency: categorical variable, consistency/inconsistency 
	- Block: categorical variable, label-only/sentence block 
	- Consistency * Block: these two may interact 
	- add participant_ID as random effect 

LookingTimeDifference ~ Sex + CDI_Score + Sex*CDI_Score + (1 | Participant_ID)
	- LookingTimeDifference: looking time in inconsistency trials - looking time in consistency trials 
	- Sex: categorical variable, F/M
	- CDI_Score: continuous variable, scored by CDI form 
	- Sex*CDI_Score: these two may interact, girls might do better than boys
	
	    return (coef(glm(Gender~Flanker_Unadj,data=dataset,subset = index, family=binomial(link='logit'))))


##Generate dataset:

```{r}

# use the parameters generated by current data 
betas  = c(23.69, -7.29,-1.32,-0.82,-1.48,1.99)
# I don't really know where can I find these SD? The regression model 
sds = c(0.2,0.2,0.2,0.2,0.2,0.2)

simulate_data <- function(num_subjects, num_trials,trial_SD, model_Beta, model_SD){
  
  intercept = model_Beta[1]
  Age_Beta = model_Beta[2]
  Sex_Beta = model_Beta[3]
  blockType_Beta = model_Beta[4]
  consistencyType_Beta = model_Beta[5]
  interaction_Beta = model_Beta[6]
  
  intercept_SD = model_SD[1]
  Age_SD = model_SD[2]
  Sex_SD = model_SD[3]
  blockType_SD = model_SD[4]
  consistencyType_SD = model_SD[5]
  interaction_SD = model_SD[6]
  
  subjects_intercepts <- rnorm(num_subjects, intercept, intercept_SD)
  subjects_Age <- rnorm(num_subjects, Age_Beta, Age_SD)
  subjects_Sex <- rnorm(num_subjects, Sex_Beta, Sex_SD)
  subjects_blockType <- rnorm(num_subjects, blockType_Beta, blockType_SD)
  subjects_consistencyType <- rnorm(num_subjects, consistencyType_Beta, consistencyType_SD)
  subjects_interaction <- rnorm(num_subjects, interaction_Beta, interaction_SD)
  
  generated_data <- data.frame(gen_subject = 1:num_subjects, 
                               gen_intercept = subjects_intercepts,
                               gen_Age_Beta = subjects_Age,
                               gen_Sex_Beta = subjects_Sex,
                               gen_blockType_Beta = subjects_blockType,
                               gen_consistencyType_Beta = subjects_consistencyType,
                               gen_subjects_interaction = subjects_interaction)
  generated_data %>% 
    nest(-gen_subject, .key = parameters) %>% 
  mutate(young_female_label_inconsistent = map(parameters, ~rnorm(num_trials, intercept+Age_Beta+consistencyType_Beta+interaction_Beta,trial_SD)),
         young_female_label_consistent = map(parameters, ~rnorm(num_trials, intercept+Age_Beta+interaction_Beta,trial_SD)),
         young_female_sentence_inconsistent = map(parameters, ~rnorm(num_trials, intercept+Age_Beta+blockType_Beta+consistencyType_Beta+interaction_Beta,trial_SD)),
         young_female_sentence_consistent = map(parameters, ~rnorm(num_trials, intercept+Age_Beta+blockType_Beta+interaction_Beta,trial_SD)),
         young_male_label_inconsistent =  map(parameters, ~rnorm(num_trials, intercept+Age_Beta+Sex_Beta+consistencyType_Beta+interaction_Beta,trial_SD)),
         young_male_label_consistent = map(parameters, ~rnorm(num_trials, intercept+Age_Beta+Sex_Beta+interaction_Beta,trial_SD)),
         young_male_sentence_inconsistent = map(parameters, ~rnorm(num_trials,
                                                                 intercept+Age_Beta+Sex_Beta+blockType_Beta+consistencyType_Beta+interaction_Beta,trial_SD)),
         young_male_sentence_consistent = map(parameters, ~rnorm(num_trials, intercept+Age_Beta+Sex_Beta+blockType_Beta+interaction_Beta,trial_SD)),
         old_female_label_inconsistent = map(parameters, ~rnorm(num_trials, intercept+consistencyType_Beta+interaction_Beta,trial_SD)),
         old_female_label_consistent = map(parameters, ~rnorm(num_trials, intercept+interaction_Beta,trial_SD)),
         old_female_sentence_inconsistent = map(parameters, ~rnorm(num_trials, intercept+blockType_Beta+consistencyType_Beta+interaction_Beta,trial_SD)),
         old_female_sentence_consistent = map(parameters, ~rnorm(num_trials, intercept+blockType_Beta+interaction_Beta,trial_SD)),
         old_male_label_inconsistent = map(parameters, ~rnorm(num_trials, intercept+Sex_Beta+consistencyType_Beta+interaction_Beta,trial_SD)),
         old_male_label_consistent = map(parameters, ~rnorm(num_trials, intercept+Sex_Beta+interaction_Beta,trial_SD)),
         old_male_sentence_consistent = map(parameters, ~rnorm(num_trials,
                                                                 intercept+Sex_Beta+blockType_Beta+consistencyType_Beta+interaction_Beta,trial_SD)),
         old_male_sentence_inconsistent = map(parameters, ~rnorm(num_trials, intercept+Sex_Beta+blockType_Beta+interaction_Beta,trial_SD))) %>% 
  unnest_legacy(young_female_label_consistent,
                young_female_label_inconsistent,
                young_female_sentence_consistent,
                young_female_sentence_inconsistent,
                young_male_label_consistent,
                young_male_label_inconsistent,
                young_male_sentence_consistent,
                young_male_sentence_inconsistent,
                old_female_label_consistent,
                old_female_label_inconsistent,
                old_female_sentence_consistent,
                old_female_sentence_inconsistent,
                old_male_label_consistent,
                old_male_label_inconsistent,
                old_male_sentence_consistent,
                old_male_sentence_inconsistent,
                .drop = FALSE)  %>% 
  unnest_legacy(parameters) %>% 
  gather(condition, lookingtime, young_female_label_consistent:old_male_sentence_inconsistent)-> data_generated

  data_generated %>% 
    mutate(
      age = ifelse(grepl("young", condition), "young", "old"),
      sex = ifelse(grepl("female",condition), "F", "M"),
      block = ifelse(grepl("label",condition),"label","sentence"), 
      consistency = ifelse(grepl("inconsistent",condition), "inconsistent","consistent")
    ) -> data_generated
  
return(data_generated)  
}

try <- simulate_data(20, 1, 1.5, betas, sds)
try %>% 
  group_by(age, sex) %>% 
  summarise(n = n())
```

```{r}
library(lme4)
run_analysis <- function(data) {
    # fit null and alternative model
    m0 <- lmer(lookingtime ~ 1 + (1 | gen_subject), data=data, REML=FALSE, control=lmerControl(calc.derivs = FALSE))
    m1 <- lmer(lookingtime ~ age + sex + consistency + block + consistency * block + (1 | gen_subject), data=data, REML=FALSE, control=lmerControl(calc.derivs = FALSE))
    #You can replace with change in AIC or a p-value for a likelihood ratio statistic
    m_bic <- BIC(m0, m1)$BIC
    statistic <- diff(m_bic)
    return(statistic)
}

repeat_analysis <- function(num_simulations, num_subjects, num_trials,trial_sd, model_Beta, model_SD) {
    bic_diffs <- c() # empty vector to store delta BICs from each simulation
    # loop for repeating the simulation
    for (i in 1:num_simulations) {
        data <- simulate_data(num_subjects, num_trials,trial_sd, model_Beta, model_SD)
        bic_diff <- run_analysis(data)
        bic_diffs <- c(bic_diffs,bic_diff) # add the current p.value to the vector
    }
    
    # calculate how many of the simulations had significant results
    power <- mean(bic_diffs <= -20) #strong evidence, see Raftery & Kass 1995
    return(list(power = power, bic_diffs = bic_diffs))
}


dat <- expand.grid(num_subjects = c(16,24,32,40), num_trials = c(1,2,3,4))
dat$id <- 1:nrow(dat)

results <- dat  %>% 
    nest_legacy(-id, .key = 'parameters')  %>% 
    mutate(power = map(parameters, ~ repeat_analysis(500, .$num_subjects, .$num_trials, 0.2, betas,sds)$power))  %>% 
    unnest_legacy(parameters, power)

results
```
 
 
```{r}
options(repr.plot.width=6, repr.plot.height=4)
results %>% 
ggplot(aes(x=num_subjects, y=power, color=as.factor(num_trials))) +
    geom_point() +
    geom_line() +
    geom_hline(yintercept = 0.8) +
    geom_hline(yintercept = 0.95) +
    scale_color_discrete('Number of trials per subject') +
    scale_x_continuous('Number of subjects') +
    scale_y_continuous('Statistical power (for Delta BIC <= -20)') +
    theme_classic()
```
 
 